Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
time-scattering -> scattering

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for the MFCC and the time-scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for the time-scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

Outcomes for the time-scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the logarithmic compression. \gl{une idée du pourquoi ?}

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
                    & time-scattering & time-scattering & mfcc \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
ei (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
ei (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
li (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
li (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-c         & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-a         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-w         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{FYW: best results for object-based approach with majority vote (on the centroids / on the centroids + on the frames) is circa 75\%}
\end{center}
\end{table}

\subsection{MFCC \vs Time scattering}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASS: $p@k$ obtained for MFCCs and scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASS: $p@k$ obtained for scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

Outcomes for the scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{ei} without the logarithmic compression. \gl{une idée du pourquoi ?}

@@

\begin{table}
\begin{center}
\begin{tabular}{llll}
                    & scattering & scattering & MFCCs \\
                    & w/ log comp.    & w/o log comp.   &      \\
             \hline
ei (linear)  & 66 (11)        & 62 (6)  & 46 (8)    \\
ei (RBF)     & 60 (7)         & 57 (8)  & 60 (8)    \\
li (linear)  & 75 (5)         & 70 (8)  & 63 (8)   \\
li (RBF)     & 78 (6)         & 73 (8)  & 72 (10)   \\
ob-c         & 66 (7)         & 58 (6)  & 56 (9)   \\
ob-a         & 61 (7)         & 54 (8)  & 61 (9)   \\
ob-w         & 54 (11)        & 43 (10) & 51 (15)   \\
\end{tabular}
\caption{FYW: best results for object-based approach with majority vote (on the centroids / on the centroids + on the frames) is circa 75\%}
\end{center}
\end{table}

\subsection{MFCC \vs scattering}
